{ \fontfamily{ptm}\selectfont Nesterov's First Order Method Accelerations: Unifications, Applications and Numerial Experiments }

### 2025-02-04 Notebook LaTEX/Proposal/proposal.tex
>w<, changes

\usepackage{ifthen}\newboolean{draftmode}\setboolean{draftmode}{true}
\input{presets/wang/input.tex}
\input{presets/misc.tex}
\input{presets/julia_lstlisting.tex}

@@

@@

\section{Catalyst accelerations}\label{sec:catalyst}
    We introduce assumptions and notations for the Catalyst Meta Acceleration Frameworks. 
    \begin{assumption}\label{ass:catalyst1}
        Given any $\beta > 0$ and $y \in \RR^n$, and $F: \RR^n\rightarrow \overline \RR$ is $\mu \ge 0$ strongly convex and closed. 
        Assume that minimizer exists for $F$ and the minimum is $F^*$. 
        For all $x,y\in \RR^n, \beta > 0$ define the model function: 
        \begin{align*}
            \mathcal M^{\beta^{-1}}_F(x; y) &:= 
            F(x) + \frac{\beta}{2}\Vert x - y\Vert^2.
        \end{align*}
        We define the Moreau Envelope at $y \in \RR^n$ to be $\mathcal M^*_{F,\beta^{-1}}(y) := \min_{x\in \RR^n} \mathcal M_F^{\beta^{-1}}(x; y)$ and the resolvent operator for subgradient of $F$ to be $\mathcal J_{\beta^{-1}F}$, i.e: which is also called the proximal operator. 
    \end{assumption}
    \begin{definition}[Absolute termination criterion C1]\label{def:catalyst-termination-c1}
        Take $F$ as given by Assumption \ref{ass:catalyst1}.
        For $\epsilon > 0, \kappa > 0$ and $x \in \RR^n$, the absolute criterion C1 characterizes the set of inexact proximal iterates by: 
        \begin{align*}
            \mathcal J_{\kappa^{-1} F}^\epsilon (x) := 
            \left\lbrace
                y \in \RR^n \left | \; 
                        \mathcal M^{1/\kappa}_F (y; x) - 
                        \mathcal M^*_{F, 1/\kappa}(x) \le \epsilon
                \right.
            \right\rbrace. 
        \end{align*}
    \end{definition}
    \begin{remark}
        Setting $\epsilon = 0$, we have the exact definition of the exact resolvent given as $\mathcal J_{\beta^{-1}}y = \mathcal J^0_{\beta^{-1}}y$. 
    \end{remark}
    \textbf{The remainder of this section is organized as the follow}. 
    Section \ref{ssec:catalyst-intro} gives the main ideas behind the Catalyst Acceleration Framework. 
    It follows Lin et al.'s first paper \cite{lin_universal_2015} on Catalyst Acceleration and summarizes the convergence analysis of the algorithm. 
    Section \ref{ssec:catalyst-second-paper} introduces Lin et al.'s second paper \cite{lin_catalyst_2018} on Catalyst which considers the improved relative error condition stated in Definition \ref{def:catalyst-termination-c2}. 
    The relative error condition improves the overall complexity and inspired nonconvex gradient based 4WD Catalyst by Paquette \cite{paquette_catalyst_2018}.

@@

        Inspired by accelerated proximal point Method (APPM) from Güler \cite{guler_new_1992}, and Inexact Proximal Point Method (IPPM) of Rockafellar 1976 \cite{rockafellar_monotone_1976}, Lin et al. \cite{lin_universal_2015} proposed a generic method taking inspirations from the convergence claims of (APPM) to accelerate Variance Reduced Method (VRM). 
        The fact that VRMs are incremental method that is not slower than full gradient descent in complexity is most relevant to our discussion. 

@@

        Let's assume for simplicity of discussion that it's deterministic, so we focus on: $F(x_k) - F^*$. 

@@

        In each iteration, it accesses the gradient of a few samples are used to attain a new estimate of the gradient with minimum additional calculations.  

@@

        Typically, an iterative scheme (i.e: VRM) with a known complexity is assigned to find inexact proximal iterates $x_k \in {\mathcal J}_{\kappa^{-1}F}^{\epsilon_k} (y_{k - 1})$. 

@@

        The total iteration complexity of Catalyst counts the total number of inner loop iteration given  the number of outer loop iterations. 

@@

            The same convergence claims hold if smaller value of $\epsilon_k$ is taken, Theorem \ref{thm:err-seq-outer-s-cnvx}, \ref{thm:erro-seq-outer-cnvx} gives the largest possible absolute error sequence $(\epsilon_k)_{k \ge 0}$ such that the convergence claim holds. 

@@

            It's poses no theoretical concerns, but it's of upmost practical concern since $F^*$ may not be accessible in practice prior to executing the algorithm. 

@@

                This assumption is legitimate for example VRMs discussed earlier. 
                See Section \ref{ssec:catalyst-future} for concerns regarding this assumption. 

@@

            If $\mu > 0$, so Proposition \ref{prop:inner-loop-complexity-s-cnvx} gives total number of inner iteration is bounded by $m \le T_{\mathbb M}k$. 

@@

            In both cases, the convergence rate remains in the same big O class as measure by the total number of $\mathbb M$.

@@

            The following results are proved in Lin et al. second Catalyst paper \cite{lin_catalyst_2018}. 

@@

            Then

@@

            Similarly, if $z \in \widetilde{\mathcal J}_{\kappa^{-1}F}^\delta(x)$, define the relative inexact gradient mapping $\widetilde{\mathcal G}_{\kappa^{-1}F}^\delta(x) = \kappa(x - z)$, we have: 

@@

            These results are instrumental to prove the convergence of $\mathbb M$ and giving convergence claim of $\mathbb A$ under certain assumption on $(\delta_k)_{k \ge 0}, (\epsilon_k)_{k \ge0}$. 
            For a more general development of characterizations of inexact oracles that is more comprehensive and rigorous, see Devolder et al. \cite{devolder_first-order_2014}. 

@@

            \todoinline{Show that there are other literatures that may also be relevant to this research question. }   

@@

            As a secondary objective, they introduced and stated the relations between several weakened characterizations of strong convexity on a closed convex set. 
            Definition 1, 2, 3, 4, 5, introduced the ideas of: Quasi-strong convexity, Quadratic under approximation, Quadratic gradient growth, quadratic functional growth (recall that it was stated as a consequence of strong convexity in Lemma \ref{lemma:q-growth}), and Global error bound conditions. 
            The content of their paper is very in-depth hence for our interests, we focus on their comments on the first Catalyst paper by Lin et al. \cite{lin_universal_2015}. 

@@

            Paquette et al. \cite{paquette_catalyst_2018} were inspired by \cite{ghadimi_accelerated_2016} and showed that the Catalyst algorithm with a different Termination criterion C2 that is based on the gradient (see equation (13), (14) in their paper) can adapt to nonconvex settings to convergence on the norm of the gradient. 
            However, it's at the expense of one additional evaluation of the proximal point method, and it requires knowledge of the function value for the outer loop. 

@@

            Attaining stronger convergence results on iterates, convergence to stationarity and function value for Nesterov's accelerated gradient methods in general requires intense amount of works. 
            In fact, these type of convergences remains nontrivial in the convex settings in general. 
            See Bauchke et al. for example, when the minimizer of $F$ doesn't exist. 

@@

            The relationship between Polyak and Nesterov momentum acceleration remains a non-trivial topics. 
            In fact, both type of acceleration can present at the same time, see 

@@

                \item Nesterov's accelerations and with inexact gradient oracles. 

            \todoinline{
                Recent development regarding the theories of accelerated proximal point method. 
                    \item Paquette et al. \cite{paquette_catalyst_2018}. 
                    \item Ghadimi and Lan, ``Accelerated gradient methods for nonconvex nonlinear and stochastic programming". 
                    \item ``Study of the behavior of Nesterov Accelerated Gradient in a nonconvex setting: the strongly quasar convex case."
                    \item Bu, Mesbashi ``A Note on Nesterov's Accelerated Method in Nonconvex Optimization: a Weak Estimate Sequence Approach''. 
                    \item Bauscke et al. ``Applying FISTA to optimization problems (with or) without minimizers"

@@

            This is a detail in the Catalyst framework, and it may not be obvious to the readers that the complexity assumption is sufficient to accommodates objective functions $F$ to be the class of all $L$-Lipschitz smooth function. 
            The entire section will: 

@@

                \item show that removing the assumption will yield non-trivial answers for the complexity analysis of Catalyst as a whole by existing theorems in the Nesterov's lower bound complexity results for black box smooth/nonsmooth objectives;
                \item show that some other the existing literatures that seems to hold the answer but actually doesn't address the question; 
                \item discuss potential relevant literatures to addressing the question. 

@@

            Schmidt et al. \cite{schmidt_minimizing_2017} also requires Lipschitz smoothness for the non-smooth part of a composite objective. 

@@

            A careful reader should realize that Assumption \ref{ass:linear-convergence-inner-loop} encapsulates the Lipschitz smoothness assumption of VRMs. 
            Furthermore, such an assumption is optimistic for the complexity of $\mathbb M$. 
            Recall that with Lipschitz smoothness and strong convexity, a lower bound of exponential rate of convergence is established by Theorem 2.1.13 in Nesterov's book \cite{nesterov_lectures_2018}. 
            Removing the smoothness assumption for $\mathbb M$, the lower bound on convergence rate of any first order algorithm becomes $\mathcal O(1/k)$ by Theorem 3.2.5 for nonsmooth function that is strongly convex. 
            From a complexity theory point of view, Catalyst acceleration didn't attempt at narrowing the lower complexity bound for functions that are convex and nonsmooth and lack of any exact proximal oracle. 
            It is absolutely possible that, for any black box nonsmooth optimization problem, the same lower bound convergence rate $\mathcal O\left(1/\sqrt{k}\right)$ as stated in Theorem 3.2.1 in Nesterov's book \cite{nesterov_lectures_2018} is true for Catalyst. 
            Unfortunately it is absolutely nontrivial to see that is true because $\mathbb A$ optimizes Moreau Envelope $\mathcal M^*_{\kappa^{-1}F}(x)$ through inexact evaluation and the Moreau Envelope has Lipschitz gradient. 

@@

            Whatever the true answer is, it's not obvious. 

@@

                Suppose that the objective function $F$ is no $L$-Lipschitz continuous hence Assumption \ref{ass:linear-convergence-inner-loop} is false. 
                If we assume that $F$ is any convex function (potentially nonsmooth and without any smooth parts), would there exist any kind of regularization parameters $(\kappa_k)_{k \ge 0}$, error sequence $\epsilon_k$ such that the overall complexity of Catalyst retains convergence rate equals or faster than $\mathcal O\left(1/\sqrt{k}\right)$ (The lower bound of all first order blackbox convex optimization)? 

@@

            If the answer is that it can be faster than the lower bound, then we had extended the Catalyst Framework, otherwise, it leads to the unintuitive result that lower bound $\mathcal O(1/\sqrt{k})$ still holds. 
            To the best of our knowledge, nobody has yet answered the question directly in the literature, but we found some relevant literatures after some preliminary research. 
            Nesterov 2014 \cite{nesterov_universal_2015}, he considers the method of accelerated gradient for function with Holder continuous gradient.
            Nesterov continued and expanded on the results obtained by Devolder et al. 2014 \cite{devolder_first-order_2014} on inexact oracles for blackbox optimizations which showed that the inexact oracle for Lipschitz smooth function can be viewed as exact for another perturbed function with Holder continuous gradient. 
            He proposed three first order algorithms where the last one, a variant of accelerated gradient method that converges optimally for all functions with Holder continuous gradient without knowing the Holder continuity constant in advance. 

@@

            In a more recent development, 
            Of course, the class of holder continuous gradient doesn't encapsulate the class of all convex function where inexact proximal point can be applied.

            \todoinline{Add research plans and literature reviews here. }

        \subsubsection{Applications for Catalyst Accelerations and its variants}
            \todoinline{
                Considers some specific applications of the Catalyst Acceleration method in the literatures. 
            }

>>>>

\usepackage{ifthen}\newboolean{draftmode}\setboolean{draftmode}{false}
\input{presets/wang/input.tex}
\input{presets/misc.tex}
\input{presets/julia_lstlisting.tex}

@@

    Here, NAG stands for Nesterov's Accelerated Gradient. 
    It refers to a general class of momentum method where the gradient are evaluated on an extrapolated iterate using the previous two iterates. 

@@

\section{Catalyst accelerations}\label{sec:catalyst}
    We introduce assumptions and notations for the Catalyst Meta Acceleration Frameworks. 
    \begin{assumption}\label{ass:catalyst1}
        Given any $\beta > 0$ and $y \in \RR^n$, and $F: \RR^n\rightarrow \overline \RR$ is $\mu \ge 0$ strongly convex and closed. 
        Assume that minimizer exists for $F$ and the minimum is $F^*$. 
        For all $x,y\in \RR^n, \beta > 0$ define the model function: 
        \begin{align*}
            \mathcal M^{\beta^{-1}}_F(x; y) &:= 
            F(x) + \frac{\beta}{2}\Vert x - y\Vert^2.
        \end{align*}
        We define the Moreau Envelope at $y \in \RR^n$ to be $\mathcal M^*_{F,\beta^{-1}}(y) := \min_{x\in \RR^n} \mathcal M_F^{\beta^{-1}}(x; y)$ and the resolvent operator for subgradient of $F$ to be $\mathcal J_{\beta^{-1}F}$, i.e: which is also called the proximal operator. 
        \par
        We invent this notations because there are no consistent notations in the literatures and several of the Catalyst papers all use dratically different notations.  
    \end{assumption}
    \begin{definition}[Absolute termination criterion C1]\label{def:catalyst-termination-c1}
        Take $F$ as given by Assumption \ref{ass:catalyst1}.
        For $\epsilon > 0, \kappa > 0$ and $x \in \RR^n$, the absolute criterion C1 characterizes the set of inexact proximal iterates by: 
        \begin{align*}
            \mathcal J_{\kappa^{-1} F}^\epsilon (x) := 
            \left\lbrace
                y \in \RR^n \left | \; 
                        \mathcal M^{1/\kappa}_F (y; x) - 
                        \mathcal M^*_{F, 1/\kappa}(x) \le \epsilon
                \right.
            \right\rbrace. 
        \end{align*}
    \end{definition}
    \begin{remark}
        Setting $\epsilon = 0$, we have the exact definition of the exact resolvent given as $\mathcal J_{\beta^{-1}}y = \mathcal J^0_{\beta^{-1}}y$. 
    \end{remark}
    \textbf{The remainder of this section is organized as the follow}. 
    Section \ref{ssec:catalyst-intro} gives the main ideas behind the Catalyst Acceleration Framework. 
    It follows Lin et al.'s first paper \cite{lin_universal_2015} on Catalyst Acceleration and summarizes the convergence analysis of the algorithm. 
    Section \ref{ssec:catalyst-second-paper} introduces Lin et al.'s second paper \cite{lin_catalyst_2018} on Catalyst which considers the improved relative error condition stated in Definition \ref{def:catalyst-termination-c2}. 
    The relative error condition improves the total complexity and inspired nonconvex gradient based 4WD Catalyst by Paquette et al. \cite{paquette_catalyst_2018}.

@@

        Inspired by accelerated proximal point Method (APPM) from Güler \cite{guler_new_1992}, and Inexact Proximal Point Method (IPPM) of Rockafellar 1976 \cite{rockafellar_monotone_1976}, Lin et al. \cite{lin_universal_2015} proposed a generic method taking inspirations from the convergence claims of APPM to accelerate Variance Reduced Method (VRM). 
        VRMs are incremental method that is not slower than full gradient descent in complexity. 

@@

        Let's assume for simplicity of discussion that it's deterministic, so from now on we focus on: $F(x_k) - F^*$ instead. 

@@

        In each iteration, it accesses the gradient of a few samples to attain a new estimate of the gradient with minimum additional calculations.  

@@

        Typically, an iterative scheme (e.g: VRM) with a known complexity finds inexact proximal iterates $x_k \in {\mathcal J}_{\kappa^{-1}F}^{\epsilon_k} (y_{k - 1})$. 

@@

        The overall iteration complexity of Catalyst algorithm counts the total number of inner loop iteration at the $k$ th iteration of outer loop. 

@@

            Theorem \ref{thm:err-seq-outer-s-cnvx}, \ref{thm:erro-seq-outer-cnvx} gives the largest possible absolute error sequence $(\epsilon_k)_{k \ge 0}$ such that the convergence claim holds. 

@@

            It's poses no theoretical concerns, but it's of upmost practical concern since $F^*$ is not accessible in practice prior to executing the algorithm. 

@@

                VRMs listed earlier statsifies this assumption. 
                Details about the consequence of this assumption is in Section \ref{ssec:catalyst-future}. 

@@

            Let $k \in \N$ be the total number of iterations experienced by the outer loop $\mathbb A$, let $m$ be the total number of iterations underwent by $\mathbb M$. 
            If $\mu > 0$, then Proposition \ref{prop:inner-loop-complexity-s-cnvx} gives the total number of inner iteration upper bound: $m \le T_{\mathbb M}k$. 

@@

@@

            The following results are proved in Lin et al. second Catalyst paper \cite{lin_catalyst_2018} in Lemma 2 and the discussions that follow it. 

@@

            Then it satsifies: 

@@

            Similarly, if $z \in \widetilde{\mathcal J}_{\kappa^{-1}F}^\delta(x)$, define the relative inexact gradient mapping $\widetilde{\mathcal G}_{\kappa^{-1}F}^\delta(x) := \kappa(x - z)$, we have: 

@@

            These results are instrumental to proving the convergence of $\mathbb M$ and giving convergence claim of $\mathbb A$ under certain assumption on $(\delta_k)_{k \ge 0}, (\epsilon_k)_{k \ge0}$. 
            For a more general, rigorous and comprehensive development of the characterizations on inexact oracles, see Devolder et al. \cite{devolder_first-order_2014}. 

@@

            % \todoinline{Show that there are other literatures that may also be relevant to this research question. }   

@@

            As a secondary objective, they introduced the relations between several weaker characterizations of strong convexity on a closed convex set. 
            Definition 1, 2, 3, 4, 5, introduced the ideas of: Quasi-strong convexity, Quadratic under approximation, Quadratic gradient growth, quadratic functional growth (recall that it was stated as a consequence of strong convexity in Lemma \ref{lemma:q-growth}), and Global Error bound conditions. 
            For our interests, we focus on one of their comments on the Catalyst by Lin et al. \cite{lin_universal_2015}. 

@@

            Paquette et al. \cite{paquette_catalyst_2018} were inspired by \cite{ghadimi_accelerated_2016} and showed that the Catalyst algorithm based on the gradient termination criterion analogous similar to C2 (see equation (13), (14) in their paper) can adapt to nonconvex settings and the norm of the gradient converges. 
            However, it's at the expense of one additional evaluation of the proximal point method, and it requires evaluating the function value once per outer loop iteration. 

@@

            Attaining stronger convergence results on iterates, convergence to stationarity and function value for NAG in general requires intense amount of works. 
            In fact, these type of convergences claims are nontrivial in the convex settings in general as well. 
            For example, see Bauchke et al. \cite{bauschke_applying_2020}, when the minimizer of $F$ doesn't exist. 

@@

            Polyak momentum (also referred to as heavy-ball inertia in the literatures) differs from Nesterov's acceleration by evaluating the gradient at the current iterates and does the extrapolation after the gradient evaluation. 
            The relationship between Polyak and Nesterov momentum acceleration remains non-trivial. 
            In fact, both type of acceleration can present at the same time, see Maulén and Peypouquet \cite{maulen_speed_2023}.
            It is sometime referred to as ``Hessian Damping" in the literatures.  

@@

                \item Nesterov's accelerations or some other first order acceleration method with inexact oracles. 
            To the best of our interpretation of Catalyst is through the theories of inexact proximal point because NAG is not the unque option and other acceleration techniques can be used as well. 
            For example, see Cai et al. \cite{cai_variance_2023} for inexact Halpern acceleration for solving variational inequalities. 
            Therefore, the theories of inexact proximal point and the algorithm used to evaluate lies deeper in the theoretical aspect of Catalyst. 
            We now list new developments for Nesterov's acceleration in the nonconvex settings with stronge convergence claim. 
            Preprint by Hermant et al. \cite{hermant_study_2024} present results that the fixed momentum variant of NAG has linear convergence  on the class of strongly quasar convex functions. 
            Preprint by Bu, Mesbashi \cite{bu_note_2020} discusses using an idea called weak estimating sequence to show the linear convergence of NAG for weakly quasi-strongly-convex functions. 
            The perspectives on how to generalize NAG to the nonconvex settings are diverse, and the issue is compounded by the fact that many variants of NAG also exist. 
            For theories of inexact proximal point method see Khanh et al. \cite{khanh_inexact_2025} for an algorithmic framework of inexact proximal point method on weakly convex function. 
            The class of weakly convex function is particularly interesting because it has general convergence claim in Ghadimi and Lan \cite{ghadimi_accelerated_2016}, and in Chapter 4 of the book preprint by Recht and Wright \cite{recht_optimization_nodate}. 
            It's unclear how their convergence theories can be combined with NAG in the non-convex case, but it's worth investigating. 
            % \todoinline{
            %     Recent development regarding the theories of accelerated proximal point method. 
            %     \begin{enumerate}
            %         \item Paquette et al. \cite{paquette_catalyst_2018}. 
            %         \item Ghadimi and Lan, ``Accelerated gradient methods for nonconvex nonlinear and stochastic programming". 
            %         \item Hermant et al. ``Study of the behavior of Nesterov Accelerated Gradient in a nonconvex setting: the strongly quasar convex case."
            %         \item Bu, Mesbashi ``A Note on Nesterov's Accelerated Method in Nonconvex Optimization: a Weak Estimate Sequence Approach''. 
            %         \item Bauscke et al. ``Applying FISTA to optimization problems (with or) without minimizers".
            %         \item Maulén and Peypouquet, ``A speed restart scheme for a dynamics with hessian-driven damping''. 
            %         \item  Cai et al. ``Variance Reduced Halpern Iteration for Finite-Sum Monotone Inclusions"
            %         \item Khanh at al. ``Inexact proximal methods for weakly convex functions''. 
            %     \end{enumerate}
            % }

@@

            This is a detail in the Catalyst framework, and it may not be obvious to the readers that the complexity assumption is sufficient to accommodate objective functions $F$ to be the class of all $L$-Lipschitz smooth function. 
            The remaining of this section will: 

@@

                \item show that removing the assumption will yield non-trivial answers for the total complexity of Catalyst because theorems Nesterov's lower bound complexity results for black box smooth/nonsmooth objectives can't be applied to Catalyst as a whole;
                \item show that some other the existing literatures that seems to hold the answer but actually doesn't fully address the question; 
                \item discuss literatures relevant to the question. 

@@

            Schmidt et al. \cite{schmidt_minimizing_2017} also requires Lipschitz smoothness for the gradient of the objective function. 

@@

            A careful reader will realize that Assumption \ref{ass:linear-convergence-inner-loop} encapsulates the Lipschitz smoothness assumption of VRMs because the proximal point sub-problem is smooth and strongly convex and lower bound from Theorem 2.1.13 from Nesterov's book \cite{nesterov_lectures_2018} applies and it has a linear convergence rate. 
            Removing the smoothness assumption of $F$, $\mathbb M$ solves subproblem $\mathcal M_{\kappa^{-1}F}(\cdot, y_k)$ which is only strongly convex.
            Then, lower bound on convergence rate of any first order algorithm becomes $\mathcal O(1/k)$ by Theorem 3.2.5 from Nesterov's book. 
            From a complexity theory point of view, Catalyst acceleration didn't attempt at narrowing the lower complexity bound for functions that are convex and nonsmooth. 
            At the same time, the theories of lower bound on blackbox optimization also cannot be applied for Catalyst Accelerations because they are based on different computational oracles. 
            It is possible that, for any blackbox nonsmooth optimization problem, the same lower bound convergence rate $\mathcal O\left(1/\sqrt{k}\right)$ as stated in Theorem 3.2.1 in Nesterov's book \cite{nesterov_lectures_2018} is true. 
            Unfortunately it is nontrivial to see it as true because $\mathbb A$ optimizes Moreau Envelope $\mathcal M^*_{\kappa^{-1}F}(x)$ through inexact evaluation and the Moreau Envelope has Lipschitz gradient. 

@@

@@

                If we assume that $F$ is any convex function (potentially nonsmooth with gradient that are not locally Lipschitz), would there exist any kind of regularization parameters $(\kappa_k)_{k \ge 0}$, error sequence $\epsilon_k$ such that the worst case total complexity of Catalyst retains convergence rate equals or faster than $\mathcal O\left(1/\sqrt{k}\right)$ (The lower bound of all first order blackbox convex optimization)? 
                I.e: Does the idea of an inexact proximal point computational oracle lift the theoretical lower bound complexity on first order blackbox convex optimization? 

@@

            If the answer is that it can be faster than the lower bound, then we had extended the Catalyst Framework to convex function without Lipschitz smooth gradient, otherwise, it leads to the unintuitive result that lower bound $\mathcal O(1/\sqrt{k})$ still holds which will prove a concept of universality of the lower bound results for blackbox convex optimizations. 
            To the best of our knowledge, nobody has yet answered the question directly in the literature, but we found some relevant literatures nonetheless. 
            In Nesterov 2014 \cite{nesterov_universal_2015}, he considered accelerated gradient for function with Hölder Continuous gradient.
            Nesterov continued and expanded on the results obtained by Devolder et al. \cite{devolder_first-order_2014} on inexact oracles for blackbox optimizations which showed that the inexact oracle for Lipschitz smooth function can be viewed as exact for another perturbed function with Hölder Continuous gradient. 
            He proposed three first order algorithms where the last one, a variant of accelerated gradient method that converges optimally for all functions with Hölder Continuous gradient without knowing the Holder continuity constant in advance. 

@@

            A more recent development in Yang and Toh \cite{yang_bregman_2022} exposes the theories of Inexact Accelerated Bregman Proximal Point method in the context of applying it for optimal transport. 
            They showed that the lower bound remains $\mathcal O(1/k)$, and in the special case when the kernel function is strongly convex relative to some norm, the optimal convergence rate of $\mathcal O(1/k^2)$ is reached. 
            These results are consistent with Nesterov's book chapter 6 \cite{nesterov_lectures_2018} and Dragomir et al. \cite{dragomir_optimal_2022}. 
            Of course, the class of convex function with Hölder Continuous gradient (i.e: the class of function that is relatively smooth to some Bregman kernel) doesn't encapsulate the class of all convex functions where inexact proximal point is applicable. 
            The original question would remain open. 
            To tackle the problem worst case complexity problem in general, it's worth mentioning
            Performance estimation problem (PEP). 
            PEP puts the set of all convex function as their iterates, gradient, and function value and the algorithm all together into Semi-definite programming constraints (SPD) and it solves for the worst case convergence. 
            Proposed by Drori and Teboulle \cite{drori_performance_2014} is the method of PEP for worst case analysis for convex programming, they showed that QCQP (Quadratic Constrained Quadratic Program) for formulation of the first order worst case iteration complexity problem can be reduced to a SPD such that it's tight. 
            And Goujaud et al. \cite{goujaud_pepit_2024} gives a Python library with APIs\footnote{APIs: A plural acronym for Application Programming Interface.} to produce worst case convergence by simply implementing the algorithm and the program formulates the SDP and solves it in the back. 
            This library supports inexact gradient, exact/inexact proximal point, and many other computational oracles. 
            These tools help us to formulate/verify complexity results if our questions on the total complexity of Catalyst can be put into the PEP framework. 
            % \todoinline{
            %     Add research plans and literature reviews here.     
            %     \begin{enumerate}
            %         \item Yang and Toh. ``Bregman proximal point algorithm revisited: A new inexact version and its inertial variant''
            %         \item Dragomir et al. ``Optimal complexity and certification of Bregman first-order methods''
            %         \item Goujaud et al. ``PEPit: computer-assisted worst-case analyses of first-order optimization methods in Python''
            %         \item Drori and Teboulle. ``Performance of first-order methods for smooth convex minimization: a novel approach''
            %     \end{enumerate}
            % }
